---
title: "Cricket Analysis"
author: "Adarsh James"
date: "2 December 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```
## Read data

```{r, message=FALSE, warning=FALSE}
odi=read.csv("C://Users//Administrator//Downloads//datasets-master//odi-batting.csv")
library(knitr)
library(dplyr)
kable(odi[1:5,])
```

## Top ten countries 
```{r, message=FALSE, warning=FALSE}
library(knitr)
library(dplyr)
top_countries = odi %>%  group_by(Country) %>% summarise(Total_runs=sum(Runs,na.rm=T)) %>% arrange(-Total_runs)
kable(top_countries[1:10,])
```

## Playerstats
```{r, message=FALSE, warning=FALSE}
library(knitr)
library(dplyr)
playerstats = odi %>% group_by(Player) %>% summarise(totalruns=sum(Runs,na.rm=T), matches= n()) %>% arrange(-totalruns) %>% filter(matches>20)
kable(playerstats[1:10,])
```

##plyrsts
```{r}
library(knitr)
library(dplyr)
plrsts= odi %>% group_by(Player,Country) %>% summarise(totalodiruns= sum(Runs,na.rm=T), matchs= n()) %>% arrange(Country)%>% filter(matchs>30)
kable(plrsts[1:10,])

```
##  Top ten players
```{r}
library(knitr)
library(dplyr)
topplyr= odi %>% group_by(Player) %>% summarise(TOTAL_RUNS =sum(Runs,na.rm=T),Country=first(Country)) %>% arrange(-TOTAL_RUNS)
kable(topplyr[1:10, ])
```


##top ten players by total no of centuries 
```{r, message=FALSE, warning=FALSE}
top_plr_cent = odi %>% filter(Runs>99) %>% group_by(Player) %>% summarise(matchs= n()) %>% arrange(-matchs)
kable(top_plr_cent[1:10, ])
```

##top ten players by total no of ducks
```{r, message=FALSE, warning=FALSE}
top_plr_duck = odi %>% filter(Runs==0) %>% group_by(Player) %>% summarise(matchs= n()) %>% arrange(-matchs)
kable(top_plr_duck[1:10, ])
```

##top ten countries by total no of players
```{r, message=FALSE, warning=FALSE}
topcountries = odi %>% group_by(Country) %>% summarise(total_no_player= length(unique(Player))) %>% arrange(-total_no_player)

kable(topcountries[1:10,])

```
##or
```{r, message=FALSE, warning=FALSE}
topcountries2 = odi %>% group_by(Country) %>% summarise(total_no_player= n_distinct(Player)) %>% arrange(-total_no_player)

kable(topcountries2[1:10,])

```






##top ten grounds by total centuries
```{r, message=FALSE, warning=FALSE}
topgrounds = odi %>% filter(Runs>99) %>% group_by(Ground) %>% summarise(centuries = n()) %>% arrange(-centuries)
kable(topgrounds[1:10,])
```


##sachin
```{r, message=FALSE, warning=FALSE}
sachin= odi%>% filter(Player== "Sachin R Tendulkar",Runs==0)%>% summarise(player= first(Player), ducks=n())
head(sachin)
```

##sachin ducks
```{r, message=FALSE, warning=FALSE}
sachinmatches=odi%>% filter(Player=="Sachin R Tendulkar")
sachinducks= sachinmatches%>%filter(Runs==0)
verusducks=sachinducks%>% group_by(Versus)%>%summarise(ducks=n())%>% arrange(-ducks)
verusducks
```
##sachin centuries
```{r, message=FALSE, warning=FALSE}
sachinmatches=odi%>% filter(Player=="Sachin R Tendulkar")
sachincent= sachinmatches%>%filter(Runs>=100)
veruscent=sachincent%>% group_by(Versus)%>%summarise(cent=n())%>% arrange(-cent)
kable(veruscent[1:10,])
```

##no of times SACHIN MISSED 100
```{r, message=FALSE, warning=FALSE}
sachinmissed100=sachinmatches%>% filter(Runs>90,Runs<100)
kable(sachinmissed100)
```
## no of 50s
```{r, message=FALSE, warning=FALSE}
sachin50s=sachinmatches%>% filter(Runs>49,Runs<100)
kable(sachin50s)
```



## adding columns
```{r}
oditemp=odi
oditemp=oditemp %>% mutate(ducks=if_else(Runs==0,1,0))
oditemp=oditemp %>% mutate(centuries=if_else(Runs>99,1,0))
oditemp=oditemp %>% mutate(missedcenturies=if_else(Runs>90 & Runs<100,1,0))
oditemp=oditemp %>% mutate(fifties=if_else(Runs>49 & Runs<100,1,0))
viewhead(oditemp)

oditemp
```


```{r}
player_summary = oditemp %>% group_by(Player)%>% summarise(totalruns=sum(Runs,na.rm=T),centuries=sum(centuries,na.rm=T),fifty=sum(fifties,na.rm=T),duck=sum(ducks,na.rm=T),Missed_centuries=sum(missedcenturies,na.rm=T))%>% arrange(-totalruns)
kable(player_summary[1:10,])
```



## convert match date to date fromat
```{r}
odi=read.csv("C://Users//Administrator//Downloads//datasets-master//odi-batting.csv")
oditemp=odi
oditemp$Date = as.Date(as.character(oditemp$MatchDate), format = "%m-%d-%Y")
str(oditemp)
oditemp=oditemp%>% mutate(YEAR= year(Date))
oditemp=oditemp %>% mutate(MONTH=month(Date))
oditemp = oditemp%>% mutate(DAY=day(Date))
oditemp= oditemp%>% mutate(DAY_OF_WEEK= weekdays(Date))
View(oditemp)
```

## yearwise centuries of sachin
```{r}

yrwisecent= oditemp %>% filter(Player=="Sachin R Tendulkar") %>% group_by(YEAR) %>% summarise(totalcenturies= sum(Centuries))%>% arrange(YEAR)
print(yrwisecent)
```

